Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Minor tweaks to intro
Small tweak to wcrqa source-target filtering results

For social cohesion and negative events, there was an extended period of time
during which RR (32nd--47th windows) and DET (35th--39th windows) were above or
nearly above chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)). These
windows span from May 3rd--14th, 2012.

>>>>

For social cohesion and negative events, there was an extended, overlapping
period of time during which RR (32nd--47th windows) and DET (35th--39th windows)
were above or nearly above chance (Figure
\@ref(fig:plot-wcrqa-source-targ-all)). These windows span from May 3rd--14th,
2012.
